Paper Summaries

### 2019-05-27 Report/Progress_Report/paper_summaries.tex
adding comments to WGAN, WGAN+GP

\subsection{Improved Training of Wasserstein GANs}
WGAN+GP \cite{Gulrajani2017}

>>>>

\subsection{Improved Training of Wasserstein GANs}
To improve the Lipschitz constraint condition to the WGANs \cite{Arjovsky2017}, an alternate method is proposed by using gradient penalty \cite{Gulrajani2017}.
Paper examines the distribution of weights with WGAN and found that weights are bunched around clipping limits.
With WGAN+GP the weights form a normal distribution, allowing more complex functions to be captured as clipped weights for a bias to simple functions, limiting the model capacity.
No batch normalization is used, as this is no longer valid when using gradient penalty.
This loss function seems to be able to train any architecture, even ResNet architectures which had currently been unsuccessful when used in GANs models.
Training speed is also improved compared with WGAN.
